Sparse Function-space Representation \\ of Neural Networks

### 2023-05-16 paper/main.tex
Wraptable
Table tuning

% Our packages
\usepackage{todonotes}
\usepackage[colorlinks=true,linkcolor=blue,allcolors=blue]{hyperref}
\usepackage{amsmath}
\usepackage{bm}
\usepackage{algpseudocode}
\usepackage{algorithm}
\usepackage{derivative}

@@

% Overview
We aim to highlight our sparse representation's ability to retain prior knowledge within a continual learning (CL) setting (as in \cref{sec:sequential}). Notably, CL methods require tuning hyperparameters, making direct comparisons difficult. We consider the setup with single-head (SH) setting that is typically hard and more competitive.
%
% Benchmarks/architectures
We consider the CL benchmarks: Sequential-MNIST (S-MNIST), Sequential-FashionMNIST (S-FMNIST), and Permuted-MNIST (P-MNIST). We follow the setups described in \cite{rudner2022continual, pan2020continual}, using a two-layer MLP with 256 hidden units and ReLU activation for S-MNIST and S-FMNIST, and a two-layer MLP with 100 hidden units for P-MNIST (full details in \cref{app:cl-exp}).

% Methods
We compare our method against two categories of methods: {\em (i)}~weight-regularization methods: EWC, SI, and VCL (which additionally incorporates coresets), and {\em(ii)}~function-based regularization methods: DER, FROMP, S-FSVI, SFR. We also introduce an ablation study where we replace $\bar{\MB}^{-1}$ with an identity matrix $\MI_M$, equivalent to assuming a GP with i.i.d.\ prior.
Following \cite{rudner2022continual}, we use 200 inducing points per tasks. Additionally,  we consider only 40 inducing points for S-MNIST, to investigate if our method was still capable of capture more information due to its sparse formulation.

%% Comments on the results:
We get the best results on S-MNIST both 40 and 200 pts. per task

@@

\begin{table}[t!] 
  \centering\scriptsize
  \caption{
  TODO: CL Experiments. $^*$ Methods relying only on weight regularization. 
  \color{blue}{Results from \cite{rudner2022continual}.} 
  %\color{red}{Preliminary results need more runs or hyperparam tuning}
  }
	\label{tbl:cl_table_1}
	% Control table spacing
	\renewcommand{\arraystretch}{1.}
	\setlength{\tabcolsep}{2pt}
	\setlength{\tblw}{0.14\textwidth}

	\input{tables/cl_table_1}
\end{table}

>>>>

% Our packages
\usepackage{todonotes}
\usepackage[colorlinks=true,linkcolor=blue,allcolors=blue]{hyperref}
\usepackage{amsmath}
\usepackage{bm}
\usepackage{algpseudocode}
\usepackage{algorithm}
\usepackage{derivative}
\usepackage{wrapfig}

@@

\setlength{\columnsep}{8pt}
\setlength{\intextsep}{0pt}
\begin{wraptable}{R}{.65\textwidth}
  \centering\scriptsize
  \caption{Continual learning experiments. We report accuracy${\pm}$std and bold based on a $t$-test. $^*$Methods rely on weight regularization.}
  %\textcolor{blue}{Results from \cite{rudner2022continual}
  %\color{red}{Preliminary results need more runs or hyperparam tuning}
	\label{tbl:cl_table_1}

	% Control table spacing
	\renewcommand{\arraystretch}{1.}
	\setlength{\tabcolsep}{1pt}
	\setlength{\tblw}{0.14\textwidth}

	\vspace*{-4pt}

	% Import table content
	\input{tables/cl_table_1}
\end{wraptable}
%
% Overview
We aim to highlight our sparse representation's ability to retain prior knowledge within a continual learning (CL) setting (as in \cref{sec:sequential}). Notably, CL methods require tuning making direct comparisons difficult. We consider the setup with single-head (SH) setting that is typically hard and more competitive.
%
% Benchmarks/architectures
We consider the CL benchmarks: Sequential-MNIST (S-MNIST), Sequential-FashionMNIST (S-FMNIST), and Permuted-MNIST (P-MNIST). We follow the setups described in \cite{rudner2022continual, pan2020continual}, using a two-layer MLP with 256 hidden units and ReLU activation for S-MNIST and S-FMNIST, and a two-layer MLP with 100 hidden units for P-MNIST (full details in \cref{app:cl-exp}).

% Methods
We compare our method against two categories of methods: {\em (i)}~weight-regularization methods: EWC, SI, and VCL (which additionally incorporates coresets), and {\em(ii)}~function-based regularization methods: DER, FROMP, S-FSVI, SFR. We also introduce an ablation study where we replace $\bar{\MB}^{-1}$ with an identity matrix $\MI_M$, equivalent to assuming a GP with i.i.d.\ prior (giving an L2 regularizer).
Following \cite{rudner2022continual}, we use 200 inducing points per tasks. Additionally,  we consider only 40 inducing points for S-MNIST, to investigate if our method was still capable of capture more information due to its sparse formulation.

%% Comments on the results:
\cref{tbl:cl_table_1} shows results
We get the best results on S-MNIST both 40 and 200 pts. per task

@@
